\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\section{Work Experience}
\subsection{{Machine Learning Researcher \hfill Sep 2020 --- Present}}
\subtext{Department of Computing Science, University of Alberta \hfill Edmonton, Alberta}
\begin{itemize}
\item Developed an API to solve optimization problems with \texttt{cvxpy, cvxopt python} for sizing of charging stations co-located with renewable energy resources. Real data is used as training data to evaluate the charging system modeling. Machine learning tools (\texttt{scipy, sklearn, pandas}) are used to extract queueing system metrics by learning from  the data.\\
supervisors: \textbf{Dr. Omid Ardakanian} and \textbf{Dr. Petr Musilek}
\item Analyzing differential privacy in Machine learning methods for smart meters. A team-led by me worked on a machine learning API for home smart meters to evaluate differential privacy mechanism.\\
supervisor: \textbf{Dr. Nidhi Hegde}

\item Led a team-based project for APIC Hackathon competion where an API was developed in \texttt{python} to detect rooftop from Google Maps using computer vision tools and recommend the best sizing requirement for installation of solar panel. The team worked interactively through \texttt{git}.

\item As a lab instructor, I developed an API in \texttt{python} to identify the anomaly in student's performance based on their experiment results and reports. 
\end{itemize}

\subsection{{Python Teaching Assistant\hfill Sep 2020 --- Dec 2020}}
\subtext{Department of Computing Science, University of Alberta \hfill Edmonton, Alberta}
\begin{zitemize}
	\item Worked collaboratively with a team of TAs to arrange the content of a 2nd-year undergraduate course on \texttt{python}.
	\item Provided solutions to the assignments and marked over 200 python coding assignments using automations (i.e \texttt{makefile}, using \texttt{python} API, bash command line etc.)
	\item Supervised undergraduate students with their python coding to improve their skills in coding and time complexity.
	\item Provided daily reports through \texttt{git}.
\end{zitemize}
%====================
% EXPERIENCE B
%====================
\subsection{{Data Science Researcher \hfill Dec 2019 --- Jun 2020}}
\subtext{Universität Stuttgart \hfill Stuttgart, Germany}
\begin{zitemize}
\item I Led three data science and probability theory projects on implementation of novel density estimation in power system analysis and using machine learning algorithms evaluate the feasibility of electric vehicle-to-grid power transaction.
\item Supervised two computer science master students with their projects on smart energy systems.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Test Tech Lead \hfill Jul 2019 --- Nov 2019}}
\subtext{Surplec HV \hfill Spruce Grove, Alberta}
\begin{zitemize}
\item Led the Test Department to detect faults and short circuits in transformers using experiment data.
\item Organized the testing environment in the department and made a structured data acquisition to capture/record/reuse the experiment data.
\item I developed an API in MS Excel to verify that running experiments on transformers follow all standards.
\end{zitemize}

\subsection{Senior Teaching Instructor \hfill Sep 2018 --- Sep 2019}
\subtext{Department of Electrical \& Computer Engineering, University of Alberta, Edmonton, Canada}
\begin{zitemize}
	\item Supervised 4 teaching assistants on delivering their work for a course in electric circuits
	\item Presented lectures on a weekly basis and clarified materials in the textbook
	\item Led students to solve their problem by providing hints and insights
\end{zitemize}

\subsection{Electrical Engineering Researcher \hfill Sep 2012 --- Sep 2015}
\subtext{Department of Power \& Control Engineering, Shiraz University, Shiraz, Iran}
\begin{zitemize}
	\item Worked at Smart Grid Laboratory at Shiraz University on the issues related to probability modeling of renewable energy sources.
	\item Developed stochastic models to apply to random events happening in a real power system.
	\item Held regular meetings with the clients from the electric regional company in Shiraz to understand our partners problem and addressing the problem at our best accuracy.
	\item Used the real world examples and data to evaluate our proposal on probabilistic modeling of the power system.
	\item The result of my work is published in a journal article [\href{https://ieeexplore.ieee.org/abstract/document/7434076}{see publication}].
\end{zitemize}


\subsection{Solar Panel Design Engineer \hfill Jan 2012 --- May 2012}
\subtext{Pars Rassam Electric}
\begin{zitemize}
	\item Worked on a contract project to equip rural road signs with solar-powered LEDs
	\item Developed a prototype for the solar electrified LED to be mounted on road signs
	\item We had regular meetings with the business client
	\item As a contractor, we had limited time to deliver the project and so time management was a key success for me
	\item The project was deployed on a rural road with more than 100 signs
\end{zitemize}

\end{document}