\documentclass[letter,11pt]{article}
\usepackage[utf8]{inputenc}

%====================
% File:         resume.tex
% Editor:       https://github.com/TimmyChan 
%               https://www.linkedin.com/in/timmy-l-chan/
% Last Updated: Nov 19, 2021
% Notes:        All formatting is done in TLCresume.sty
%               No need to touch that file. 
%               All actual content is in the sections/ folder.
%====================

\usepackage{TLCresume}

%====================
% CONTACT INFORMATION
%====================
\author{Mohammad Hadi Rouhani} % Name Here
\def\phone{(587)566-5117}
\def\city{}
\def\email{rouhani@ualberta.ca}
\def\Web{hadi2525.github.io}
% \def \LinkedIn{linkedin.com/in/hrohani} % linkedin.com/in/______
%\def\github{hadi2525} % github username
%
\def\role{} % JOB TITLE

\begin{document}
\begin{center}
	\begin{minipage}[b]{.3\textwidth}
		\raggedright
		{\large \phone} \\ % PHONE
		{\city} % City
		% EMAIL
		
	\end{minipage}%
	\begin{minipage}[b]{.4\textwidth}
		\makeatletter
		\centering {\HUGE \@author} \\
		\makeatother
		\vspace{.5em}
		{\color{highlight} \Large{\role}}
	\end{minipage}%
	\begin{minipage}[b]{.3\textwidth}
		\raggedleft 
		\href{mailto:\email}{\textbf{Email:} \email}\\ 
		\href{https://hadi2525.github.io/\Web}{\textbf{Website:} \Web}
		%	\href{https://github.com/\github}{\textbf{GitHub:} \github} \\% Portfolio 
		%	\href{https://www.linkedin.com/in/\LinkedIn}{\textbf{LinkedIn:} \LinkedIn} % LinkedIn
		%	
	\end{minipage}

%	{\color{highlight} \hrule}
\end{center}
\vspace{-1em}	
\section{Highlights}
\begin{zitemize}
	\item Skilled machine learning professional with more than three years of demonstrated works in developing ML models.
	\item Proficient in addressing complex business problems into meaningful ML solutions.
	\item Excelled at conducting cutting edge research in ML and AI.
	\item Proven history of successful collaboration with professionals to educate and develop end-to-end ML projects.
\end{zitemize}
\section{Education}
\skills{M.Sc. in Computer Science}, \textit{University of Alberta, Edmonton, Canada}	\hfill  2020 --- 2022

\skills{M.Sc. in Electrical \& Computer Engineering},  \textit{University of Alberta, Edmonton, Canada}	\hfill  2016 --- 2019
%\vspace{-0.65em}
%\begin{zitemize}
	% This may be put at the end in the achievement section 
%\end{zitemize}

\skills{B.Sc. (with distinction) in Electrical \& Computer Engineering}, \textit{Shiraz University, Shiraz, Iran} \hfill 2009 --- 2013

%\begin{zitemize}
%	\item Dean's Certificate of Honor for excellence in leadership and academic
%\end{zitemize}

\section{Skills}
\begin{tabular}{p{9em}  p{40em}}
	\skills{Tools \& Languages} &     Python (scikit-learn, pytorch, tensorflow, pandas, spark, etc.), C, Git, Linux, Coud computing platforms (Google Cloud, AWS, Docker) \\
	\skills{Web dev. tools} & Typescript, Node.js, Angular, StreamLit\\
	\skills{Quantitative topics} &   Statistics and advanced probability, Algorithms and Optimization, Markov chain, data structures, machine Learning, deep learning\\
	\skills{Communication} &  English (fluent), Persian (fluent-native), German (intermediate)
\end{tabular}

\section{Work Experience}
\subsection{Machine Learning Facilitator --- Alberta Machine Intelligence Institute (Amii), Edmonton, AB \hfill Jul 2022 --- Present}
\begin{zitemize}
	\item Develop ML curriculum materials for stakeholders
	\item Present workshops around AI and ML for businesses and clients
	\item Coordinate with the Talent teams to navigate talented individuals to their success in AI
	\item Explain end-to-end machine learning projects for general public
\end{zitemize}
\subsection{AI/ML Program Manager --- AI4Good Lab, Montreal, QC \hfill Apr 2022 --- Aug 2022}
\begin{zitemize}
	\item Helped organize a 7-week intensive workshop with more than 100 participants, teaching assistants, lecturers, guest speakers, industry mentors, etc.
	\item Managed the ML curriculum materials from classical (supervised, unsupervised) machine learning to convolutional neural networks and reinforcement learning.
	\item Delivered real world problems to exhibit ML model applications in finding solutions.
	\item Trained talented students/participants to become the future ML startup founders from underrepresented society.
\end{zitemize}
\subsection{Freelance Data Scientist \hfill Jan 2022 --- Jul 2022}
\begin{zitemize}
	\item \textbf{ML speaker} at PyYYC, PyData Calgary, and EdmontonPy - [\href{https://www.youtube.com/watch?v=4S_QGDHTICw}{\textbf{YouTube}]} \hfill May 2022
%	\item \textbf{Consultant} -  (Students analytics \& AI Capability) \hfill Apr 2022
%	\begin{zitemize}
%		\item Proposed a strategic data exploratory analysis on student performance at elementary schools in Alberta
%		\item Developed an AI-centric suggestion model for students 
%	\end{zitemize}
%	\item \textbf{Consultant} -  (oil \& gas company) \hfill Mar 2022
%	\begin{zitemize}
%		\item Conducted a comprehensive EDA to enable on-site reservoir rock analysis.
%		\item Applied several classification and clustering ML models to achieve the highest accuracy.
%	\end{zitemize}
	\item \textbf{Continuous Integration ML Deployment (ML-Ops)}~[\href{https://github.com/Hadi2525/ML_production_01/tree/Hadi2525-patch-1}{Python Code}] \hfill Feb 2022
	\begin{zitemize}
		\item Image recognition analysis with classification models.
		\item Optimized the number of estimators for the ensemble learning algorithm with 98 \% accuracy.
		\item Reduced the input feature dimension and successfully achieved a 97 \% accuracy.
		\item Developed a pipeline to run ML model in production on Github workflow using docker.
	\end{zitemize}
	\item \textbf{Pharmaceutical Drug review} -~[\href{https://github.com/Hadi2525/applied_ML/blob/master/Pharma/drug_model.ipynb}{Python Code}]\hfill Jan 2022
	\begin{zitemize}
		\item Deployed an NLP model and sentiment analysis.
		\item The trained machine learning model provided an accuracy of more than 90\%.
	\end{zitemize}

\end{zitemize}

\subsection{{Researcher --- University of Alberta, Edmonton, AB \hfill Sep 2020 --- Present}}
\begin{zitemize}
	\item Developed python applications to solve optimization problems. Designed machine learning models for time-series prediction problems.
	%	supervisors: \textbf{Dr. Omid Ardakanian} and \textbf{Dr. Petr Musilek}
	\item Deployed differential privacy in Machine learning training models. Took the leadership of a team of ML devs to evaluate differential privacy mechanism.
	\item Led a team of programmers to win the 1st runner up at summer E-Hackathon.

\end{zitemize}

\subsection{{Python Teaching Assistant --- University of Alberta, Edmonton, AB\hfill Sep 2020 --- Dec 2020}}
\begin{zitemize}
	\item Worked collaboratively with a team of TAs to organize the content of \textbf{CMPUT 274} a course in \textbf{python}.
	\item Provided solutions to assignments and marked over 200 python coding  using automation scripts.
	\item Advised undergraduate students with their coding style to improve their programming skills.
\end{zitemize}
\subsection{{ Research Advisor --- Stuttgart Universität, Germany \hfill Dec 2019 --- Jun 2020}}
\begin{zitemize}
	\item Led three projects in renewable energy and electric vehicle transportation in German electricity market.
	\item Published a professional article on electric vehicle charging policy and integration
%	\item Collaborated with a team of professionals working on deployment of a  charging station on-campus Vaihingen.
	\item Supervised a number of computer science MSc students on their projects 
%	\item Took the initiative to get involved in various projects with the department research team.
	\item Proven to be an effective team player to maintain a productive relationship between departments.
\end{zitemize}

\subsection{{Test Technician Lead --- Surplec HV,  Spruce Grove, AB \hfill Jul 2019 --- Nov 2019}}
\begin{zitemize}
	\item Supervised the transformer test department to detect anomalies in transformers from experiment data.
		\item Managed to restructure testing environment and made an automation for data acquisition of experiments.
	\item Got promoted to the lead position in less than three months (Left the job for an exciting opportunity in Germany).
\end{zitemize}

%\subsection{Residence Assistant \hfill May 2018 - August 2019}
%\subtext{Hired through multiple interview process by the University of Alberta Residence Team}
%\begin{zitemize}
%	\item Administered regular checking in with students and residents for their well-being.
%	\item Participated in on-call shifts, monitoring residence community during after hours.
%	\item Acted as an effective liason between students and Residence staff.
%\end{zitemize}

%\subsection{Energy System Researcher --- University of Alberta, Edmonton, AB\hfill Sep 2018 --- Sep 2019}
%\begin{zitemize}
%	\item Conducted extensive research on modeling and control of HVDC power electronics.
%	\item Successfully developed a novel modular multilevel converter for hybrid AC and DC applications.
%	\item Coordinated two projects that led to high impact publications.
%	\item Worked with hardware-in-the-loop real time simulators for switched-mode modeling of power electronic converters.
%	\item Nominated by the Department for the Vanier Scholarship National competition.
%	\item Helped with teaching at technical lab sessions and supervised teaching assistants on their presentation materials.
%\end{zitemize}

\section{Relevant Publications}
\begin{zitemize}
	\item \textbf{M.~H.~Rouhani}, Omid Ardakanian, and Petr Musilek, ``Robust Optimal Sizing of Electric Charging Stations equipped with renewable Energy Sources,'' \textit{IEEE Power \&  Energy Society General Meeting (PES-GM)}, 2022 [\href{https://github.com/Hadi2525/hadi2525.github.io/blob/main/papers/EV_Charging_Scheduling_Summary_Report.pdf}{\textbf{Link}}].
	
	\item \textbf{M.~H.~Rouhani}, M.~Mohammadi, and M.~Aiello, ``A Fuzzy-based Soft Clustering Probabilistic Power Flow Considering Inter-Event Time Correlation'', \textit{Electric Power Systems Research Elsevier}, 107677,  2021. [\href{https://www.sciencedirect.com/science/article/pii/S0378779621006581}{\textbf{Link}}]
	
	\item  \textbf{M.~H.~Rouhani}, M.~Mohammadi, A.~Kargarian ``Parzen Window Density Estima-tor Based Probabilistic Power Flow Considering Correlated Uncertainties,'' \textit{IEEE Transactions on Sustainable Energy}, vol. 7, no. 3, pp. 1170-1181, 2016. [\href{https://ieeexplore.ieee.org/abstract/document/7434076}{\textbf{Link}}]
	
	
	
\end{zitemize}
\section{Projects}
	
%	<\textbf{Machine learning in Medical Science}>
%	<\textbf{Machine Learning in Energy sector}>
	\subsection{Sizing of Charging Stations Co-located with Solar Panel and Battery Storage \hfill Oct 2021}
\subtext{Project sponsored by \textbf{ATCO Electric}}
\begin{zitemize}
	\item Worked on addressing the future EV transportation system.
	\item Analyzed various strategies/possibilities to provide incentives for EV owners.
	\item Solved a problem to present a fully green charging stations powered by renewables.
	\item Delivered a prototype model that is 95 \% carbon emission free.
\end{zitemize}

\subsection{Rooftop solar panel sizing detection using deep learning \hfill Jun 2021}
\subtext{Alberta power industry consortium (APIC) 2021 Hackathon Competition}
\begin{zitemize}
 \item Took the leadership of a team of programmers for APIC Hackathon competition.
	\item Developed an API to detect feasible rooftop area from Google Maps using computer vision tools and recommend the best sizing requirement. 
\end{zitemize}
%<\textbf{Computer Science course projects}>
%\subsection{C Coding in Linux~[\href{https://github.com/Hadi2525/vmemory_maps}{C Code}] \hfill Feb 2021}
%\begin{zitemize}
%	\item Developed a C programming code that shows the virtual memory allocation of a running process in Linux. 
%	\item Wrote a C code to model a secure TCP communication between a server and several clients.
%	\item Worked with Valgrind in C/Linux.
%\end{zitemize}

%<\textbf{Queueing system modeling in transportation and communication networks}>
\subsection{Simulator for systems with queues [\href{https://github.com/Hadi2525/queueing_theory}{Python Code}] \hfill Mar 2021}
\begin{zitemize}
	\item Developed an algorithm using advanced data structures model a queueing system.
\end{zitemize}


%\subsection{National Elite Researcher in Electrical Engineering \hfill Sep 2012 --- Sep 2015}
%\subtext{Electric Regional Company, Shiraz, Iran}
%\begin{zitemize}
%	\item Held regular meetings with the client to understand their problem and address the solution at our best.
%	\item Provided training and required materials to our users in the company to understand the scope of the research.
%	\item Used the real world  data to deploy my research proposal.
%\end{zitemize}


%\subsection{Solar Panel Design Consultant\hfill Jan 2012 --- May 2012}
%\subtext{Pars Rassam Electric, Shiraz, Iran}
%\begin{zitemize}
%	\item Consulted on a contract project to equip rural road signs with solar-powered LEDs
%	\item Held regular meetings with the business client to achieve their desire
%	\item Managed the deployment of prototypes on a rural road with more than 100 signs
%\end{zitemize}




% make a newpage wherever it is a clean break
% \newpage



%\section{Related Courses}
%\begin{tabular}{p{5.9cm}p{5.3cm}p{5cm}p{5cm}}
%	Computer Networks & Operating Systems (Linux) & Privacy in Machine Learning & Algorithms II\\
%	Machine Learning A-Z (Udemy) & Data Science w/ Python (IBM) & Data structure & Deep Learning \\
%\end{tabular}
%\subsection{Certificates:}
%\begin{zitemize}
%	\item Deep Learning with Andrew NG - \textbf{Coursera} \hfill Jan 2022
%	\item Machine Learning \& Deep Learning A-Z - \textbf{Udemy} \hfill May \& July 2019
%	\item Data Science with Python - \textbf{IBM Online} \hfill April 2019
%\end{zitemize}

\section{Leadership Activities}
\begin{zitemize}
	\item President and CEO of a non-profit Iranian community based in Edmonton \hfill \textbf{May 2017 --- May 2018}
	\item Hired as a Resident Community Advisor at the University of Alberta Residence \hfill \textbf{May 2017 - Aug 2018}
	\item Helped with hiring process of University of Alberta, Residence \hfill \textbf{Feb 2018}
\end{zitemize}
\section{Achievements}
\begin{zitemize}
	\item More than 80 citations for research reference in Google Scholar \hfill \textbf{Present}
	\item 1st runner up winner of APIC E-Hackathon \hfill \textbf{June 2021}
	\item Nominated for the Vanier Scholarship, the most prestigious scholarship among Canadian grad schools \hfill \textbf{Feb 2018}
	\item Dean's Certificate of Honor for excellence in leadership and academic, Shiraz University \hfill \textbf{Jul 2013}
\end{zitemize}
%\section{Achievements}
%\begin{zitemize}
%	\item 1st runner up APIC-Hackathon	\hfill Jul 2021
%	\item Ranked among the top 100 Canadian graduate students to recieve Vanier Scholarship	\hfill Winter 2018
%%	\item Reached by more than 6000 users in Stackoverflow where I hold 200 reputation points.
%	\item Recipient of Graduate Recruitment Scholarship (\$ 15000) \hfill Sep 2020
%	\item Travel Award grant from GSA (\$ 500) and FGSR (\$ 2000) \hfill Jul 2017
%	\item Recipient of the Dean's Honor Award as the top BSc Electrical Engineer Student among 164 undergrads \hfill Jul 2013
%\end{zitemize}
%%Published more than 10 papers in peer reviewed journals/conferences  \hfill ---







%Active programmer in \href{www.leetcode.com}{leetcode.com}  by solving algorithms in Python and C. \hfill ---










\end{document}


