\documentclass[letter,11pt]{article}
\usepackage[utf8]{inputenc}

%====================
% File:         resume.tex
% Editor:       https://github.com/TimmyChan 
%               https://www.linkedin.com/in/timmy-l-chan/
% Last Updated: Nov 19, 2021
% Notes:        All formatting is done in TLCresume.sty
%               No need to touch that file. 
%               All actual content is in the sections/ folder.
%====================

\usepackage{TLCresume}

%====================
% CONTACT INFORMATION
%====================
\author{Hadi Rohani} % Name Here
\def\phone{(587)566-5117}
\def\city{Department of Computing Science, University of Alberta, Edmonton, AB}
\def\email{rouhani@ualberta.ca}
\def\Web{hadi2525.github.io}
% \def \LinkedIn{linkedin.com/in/hrohani} % linkedin.com/in/______
%\def\github{hadi2525} % github username
%
\def\role{Computer Science Researcher} % JOB TITLE

\begin{document}
\begin{center}
	\begin{minipage}[b]{.3\textwidth}
		\raggedright
		{\large \phone} \\ % PHONE
		{\city} % City
		% EMAIL
		
	\end{minipage}%
	\begin{minipage}[b]{.4\textwidth}
		\makeatletter
		\centering {\HUGE \@author} \\
		\makeatother
		\vspace{.5em}
		{\color{highlight} \Large{\role}}
	\end{minipage}%
	\begin{minipage}[b]{.3\textwidth}
		\raggedleft 
		\href{mailto:\email}{\textbf{Email:} \email}\\ 
		\href{https://hadi2525.github.io/\Web}{\textbf{Website:} \Web}
		%	\href{https://github.com/\github}{\textbf{GitHub:} \github} \\% Portfolio 
		%	\href{https://www.linkedin.com/in/\LinkedIn}{\textbf{LinkedIn:} \LinkedIn} % LinkedIn
		%	
	\end{minipage}

%	{\color{highlight} \hrule}
\end{center}
\vspace{-0.75em}	
\section{Highlights}
\begin{zitemize}
	\item Three years of experience working with python programming and algorithm development
	\item Proficient in data visualization with \textbf{Tableau}, \textbf{Seaborn}, \textbf{plotly}, and \textbf{matplotlib} from Python
	\item Highly skilled in developing machine learning tools and conducting comprehensive report as a data scientist
	\item Team-player with strong communication and leadership skills gained from real experience
	\item With more than 3 years of working for Canadian and European companies
	\item I have a Canadian Permanent Residency status and so I am eligible to work full-time in Canada
\end{zitemize}

\section{Skills}
\begin{tabular}{p{10em} p{0.01em} p{40em}}
	\skills{Tools \& Languages} & &    C, Python, Git, Linux, SQL, Worked with cloud computation and ComputeCanada \\
	\skills{Quantitative topics} & &  Computer networks, algorithm, Markov process, data structure, machine Learning, deep learning\\
	\skills{Organizational skills} & & Team-oriented, public speaker, active listener, program planner and administrator\\
	\skills{Communication} & & English (fluent speaker), Persian (fluent speaker), German (reading and writing)
\end{tabular}


\section{Projects}
	<\textbf{Medical Science}>
	\subsection{1- Pharmaceutical Drug review - A machine learning \& data analysis~[\href{https://github.com/Hadi2525/applied_ML/blob/master/Pharma/drug_model.ipynb}{Python Code}]}
	\subtext{Supervised a data analysis using natural language processing and machine learning tools to analyze reviews on drugs}
	\begin{zitemize}
		\item Leveraged the data obtaining techniques from \textbf{Pandas} and visualization tools and demistify the pattern in the data.
		\item Developed \textbf{Wordcloud} package for NLP implementation and sentiment analysis
		\item The trained machine learning model provided an accuracy of more than 90\%.
	\end{zitemize}
	
	\subsection{2- Breast cancer diagnosis using Machine Learning~[\href{https://github.com/Hadi2525/applied_ML/blob/master/Breast_cancer_ML/BC_ML.ipynb}{Python Code}]}
	\subtext{Supervised Machine Learning using classification methods from Scikit-learn python}
	\begin{zitemize}
		\item Implemented 7 different classification ML models to compare diagnostic accuracy
		\item Open source code and data analysis report is available
	\end{zitemize}	
	
	<\textbf{Energy sector}>
	\subsection{1- Sizing of Charging Stations Co-located with Solar Panel and Battery Storage}
\subtext{A business project in collaboration with \textbf{ATCO Electric }company, Alberta, Canada}
\begin{zitemize}
	\item Held regular business meetings and articulate the problem as per the client's need.
	\item Translated the problem into a mathematical optimization solution
	\item Developed an API in python and provided a comprehensive solution
	\item Took the initiative to generalize the API for several similar problems and the final work was a success
\end{zitemize}



\subsection{2- Rooftop solar panel sizing detection using deep learning models~[Hackathon 1st runner up winner!]}
\subtext{Alberta power industry consortium (APIC) 2021 Hackathon Competition}
\begin{zitemize}
 \item Led a team of programmers for APIC Hackathon competition 
	\item Developed an API to detect feasible rooftop area from Google Maps using computer vision tools and recommend the best sizing requirement. 
	\item The team worked interactively in an agile framework with specs of CI/CD.
\end{zitemize}

<\textbf{Other Applied ML small projects in finance and business}>\vspace{-0.75em}
\begin{zitemize}
	\item Predicted the company employees salary using various regression models.
	\item Developed a machine learning model to predict job positions of a company.
\end{zitemize}
<\textbf{Computer Science course projects}>
\subsection{C Coding in Linux~[\href{https://github.com/Hadi2525/vmemory_maps}{C Code}]}
\begin{zitemize}
	\item Developed a C programming code that shows the virtual memory allocation of a running process in Linux. 
	\item I wrote a C code to model a secure TCP communication between a server and several clients.
	\item Working with Valgrind in C/Linux.
\end{zitemize}

\subsection{Simulator for systems with queues [\href{https://github.com/Hadi2525/queueing_theory}{Python Code}]}
\begin{zitemize}
	\item I developed an algorithm using various data structures including doubly linked lists, tensors, hash tables to model a queueing system
	\item An object-oriented programming API was developed to model customers and servers.
	\item I improved the coding so that it would have the best time complexity 
\end{zitemize}


\section{Work Experience}
\subsection{{Machine Learning Researcher \hfill Sep 2020 --- Present}}
\subtext{Department of Computing Science, University of Alberta, \hfill Edmonton, Alberta}
\begin{zitemize}
	\item Developed APIs to solve optimization problems with \texttt{cvxpy, cvxopt python}.\\
%	supervisors: \textbf{Dr. Omid Ardakanian} and \textbf{Dr. Petr Musilek}
	\item Deploy privacy in Machine learning training models. I took the leadership of a team of MLops evaluate differential privacy mechanism.\\
	supervisor: \textbf{Dr. Nidhi Hegde - Borealis AI}
	\end{zitemize}

\subsection{{Python Teaching Assistant\hfill Sep 2020 --- Dec 2020}}
\subtext{Department of Computing Science, University of Alberta, \hfill Edmonton, Alberta}
\begin{zitemize}
	\item Worked collaboratively with a team of TAs to organize the content of a course on \texttt{python}.
	\item Provided solutions to assignments and marked over 200 python coding  with automations
	\item Supervised undergraduate students with their coding style to improve their coding skills.
\end{zitemize}
\subsection{{Data Science Researcher \hfill Dec 2019 --- Jun 2020}}
\subtext{Service Computing, Univeristy of Stuttgart, \hfill Stuttgart, Germany}
\begin{zitemize}
	\item I took the leadership of three projects in data science and advanced probability theory using machine learning algorithms.
	\item Supervised a number of computer science MSc students.
	\item Practiced agile framework with scrum for research (score)
\end{zitemize}

\subsection{{Test Tech Lead \hfill Jul 2019 --- Nov 2019}}
\subtext{Surplec HV, \hfill Spruce Grove, Alberta [HQ: Sherbrooke, Quebec]}
\begin{zitemize}
	\item Supervised the Test Department to detect anomalies in transformers using experiment data.
	\item Took the initiative to revamp the testing environment and made an automation for data acquisition for experiments.
	\item My API significantly reduced the delay time in delivering test documents to the quality department.
\end{zitemize}

\subsection{Senior Teaching Instructor \hfill Sep 2018 --- Sep 2019}
\subtext{Department of Electrical \& Computer Engineering, University of Alberta, \hfill Edmonton, Canada}
\begin{zitemize}
	\item Supervised a number of teaching assistants on delivering their lectures.
	\item Organized weekly meeting to address concerns and problems with lectures and instructor notes.
	\item Assessed lectures and clarified materials for 3 classes weekly.
\end{zitemize}

\subsection{National Elite Researcher in Electrical Engineering \hfill Sep 2012 --- Sep 2015}
\subtext{Department of Power \& Control Engineering, Shiraz University, \hfill Shiraz, Iran}
\begin{zitemize}
	\item I was awarded this position due to being the top BSc student in Electrical Engineering at Shiraz University.
	\item Developed stochastic models to apply to random events happening in a real power system.
	\item Held regular meetings with the clients from the electric regional company to understand their problem and address the solution at our best.
	\item Used the real world examples and data to evaluate our proposal.
\end{zitemize}


\subsection{Solar Panel Design Engineer Consultant\hfill Jan 2012 --- May 2012}
\subtext{Pars Rassam Electric, \hfill Shiraz, Iran}
\begin{zitemize}
	\item Consulted on a contract project to equip rural road signs with solar-powered LEDs
	\item Developed a prototype for the solar powered LED mounted on road signs
	\item Held regular meetings with the business client to achieve their desire
	\item As a contractor, we had limited time to deliver the project and so time management was the key success for me
	\item The project was deployed on a rural road with more than 100 signs
\end{zitemize}


\section{Education}
\skills{M.Sc. in Computer Science}, \textit{University of Alberta, Edmonton, Canada}	\hfill Sep 2020 ---  Present

\skills{M.Sc. in Electrical Engineering}, \textit{University of Alberta, Edmonton, Canada}	\hfill Sep 2016 ---  Sep 2019

\skills{B.Sc. (with distinction) in Electrical \& Computer Engineering}, \textit{Shiraz University, Shiraz, Iran} \hfill	Sep 2009 --- Sep 2013



% make a newpage wherever it is a clean break
% \newpage



\section{Related Courses}
\begin{tabular}{p{5.9cm}p{5.3cm}p{5cm}p{5cm}}
	Computer Networks \& Performance & Operating Systems (Linux) & Privacy in Machine Learning & Algorithms II\\
	Machine Learning A-Z (Udemy) & Data Science w/ Python (IBM) & Data structure & Neural Networks \\
	Online optimization & Convex optimization (Stanford) & \multicolumn{2}{l}{Economics \& Finance in Engineering}\\
\end{tabular}
\subsection{Certificates:}
\begin{zitemize}
	\item Machine Learning with Andrew NG - \textbf{Coursera} \hfill Jan 2022
	\item Web Application with Angular - \textbf{Codewithmosh.com} \hfill Dec 2021
	\item Artificial Intelligence Foundations: Machine Learning - \textbf{LinkedIn} \hfill Dec 2021
	\item Version Control System, git - \textbf{github} \hfill Sep 2020
	\item Deep Learning A-Z - \textbf{Udemy} \hfill July 2019
	\item Machine Learning A-Z - \textbf{Udemy} \hfill May 2019
	\item Data Science with Python - \textbf{IBM Online} \hfill April 2019
\end{zitemize}



\section{Activities \& Achievements}
 	1st runner up APIC-Hackathon	\hfill Jul 2021

Ranked among the top 100 graduate students to recieve Vanier Scholarship	\hfill Winter 2018

Reached by more than 6000 users in Stackoverflow where I hold 200 reputation points. \hfill -

Active programmer in \href{www.leetcode.com}{leetcode.com}  by solving algorithms in Python and C. \hfill -

President and CEO of a non-profit Iranian community based in Edmonton \hfill May 2017 - May 2018

Recipient of Graduate Recruitment Scholarship (\$ 15000) \hfill Sep 2020 - Sep 2021

Travel Award grant from GSA (\$ 500) and FGSR (\$ 2000) \hfill Jul 2017

Recipient of the Dean's Honor Award as the top BSc Electrical Engineer Student among 164 undergrads \hfill Jul 2013
\end{document}


