\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Computer Science Researcher \hfill Sep 2020 --- Present}}
\subtext{Department of Computing Science, University of Alberta \hfill Edmonton, Alberta}
\begin{itemize}
\item Developed an API to solve convex optimization problem using \texttt{cvxpy Python} for sizing of charging stations co-located with renewable energy resources. Real data is used as training data to evaluate the charging system modeling. Machine learning tools (\texttt{scipy, sklearn, pandas}) are used to learn the data.\\
supervisors: \textbf{Dr. Omid Ardakanian} and \textbf{Dr. Petr Musilek}
\item Analyzing differential privacy in Machine learning methods for smart meters. A team-led by me worked on a machine learning API for home smart meters to evaluate differential privacy mechanism.\\
supervisor: \textbf{Dr. Nidhi Hegde}

\item Led a team-based project for APIC Hackathon competion where an API was developed in \texttt{python} to detect rooftop from Google Maps and recommend the best sizing requirement for installation of solar panel. The team worked interactively through \texttt{git}.

\item As a lab instructor, I developed an API in \texttt{python} to identify the anomaly in student's performance in their experiments. 
\end{itemize}

\subsection{{Teaching Assistant\hfill Sep 2020 --- Dec 2020}}
\subtext{Department of Computing Science, University of Alberta \hfill Edmonton, Alberta}
\begin{itemize}
	\item Worked collaboratively with a team of TAs to arrange the content of an intermediate course on python
	\item Provided solutions to the assignments and marked over 200 python coding assignments using automations (makefile, using python API, bash command line etc.)
	\item Provided daily reports through \texttt{git}.
\end{itemize}
%====================
% EXPERIENCE B
%====================
\subsection{{Data Science Researcher \hfill Dec 2019 --- Jun 2020}}
\subtext{Universität Stuttgart \hfill Stuttgart, Germany}
\begin{zitemize}
\item I Led three data science and probability theory projects on implementation of novel density estimation in power system analysis and using machine learning algorithms evaluate the feasibility of electric vehicle-to-grid power transaction.
\item Supervised two computer science master students with their projects on smart energy systems.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Test Tech Lead \hfill Jul 2019 --- Nov 2019}}
\subtext{Surplec HV \hfill Spruce Grove, Alberta}
\begin{zitemize}
\item Led the Test Department to detect faults and short circuits in transformers using experiment data.
\item Organized the testing environment in the department and made a structured data acquisition to capture/record/reuse the experiment data.
\item I developed an API in MS Excel to verify that running experiments on transformers follow all standards.
\end{zitemize}


\end{document}